The Suburbanisation of Poverty in Scotland’s Cities: Urban Regeneration or

### 2016-08-31 markdown/draft.RmD
add simd 2016; redo simd code; redo model run code; redo markdown

---
title: "The Suburbanisation of Poverty in Scotland’s Cities: Urban Regeneration or Social Cleansing?"
author: "Jon Minton & Nick Bailey"
date: "31 August 2016"
output: html_document
---

@@

```{r id_props, eval = TRUE, echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE}
simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
    distinct() %>%
    rename(City = nearest_centre) %>% 
    filter(City %in% c("Aberdeen", "Dundee", "Edinburgh", "Glasgow")) %>% 
    mutate(centralness = cut(
      distance_to_centre, 
      breaks = c(0, 8000, 20000, Inf), 
      labels = c("centre", "periphery", "exurb"))
    ) %>% 
  filter(centralness != "exurb") %>% 
  group_by(City, year, centralness) %>%
  mutate(pop_nonid = pop_total - pop_incomedeprived) %>% 
  summarise(pop_nonid = sum(pop_nonid), pop_incomedeprived = sum(pop_incomedeprived)) %>% 
  summarise(
    `Income Deprived` = pop_incomedeprived[centralness == "centre"] / sum(pop_incomedeprived),
    `Not Income Deprived` = pop_nonid[centralness == "centre"] / sum(pop_nonid)
  ) %>% 
  gather(key = "type", value = "prop", `Income Deprived`:`Not Income Deprived`) -> tmp

tmp %>% filter(type == "Income Deprived") %>% 
  ggplot(., 
         aes(
            x = year, y = prop 
            )
         ) + 
  geom_line() + geom_point() +
  facet_wrap( ~ City, nrow = 2, scales = "free_y") + 
  labs(x = "Year", y = "Proportion", title = "Proportion income deprived within 8km of Centre")

tmp %>% filter(type == "Not Income Deprived") %>% 
  ggplot(., 
         aes(
            x = year, y = prop 
            )
         ) + 
  geom_line() + geom_point() +
  facet_wrap( ~ City, nrow = 2, scales = "free_y") + 
  labs(x = "Year", y = "Proportion", title = "Proportion Not income deprived within 8km of Centre")

@@

*	Allocating Datazones to cities by defining a centroid for city, identifying the closest centroid for each Datazone and then applying a cut-off distance of around 18-20kms.

*	Converting data for 2004 to 2012 SIMDs from 2001 Datazones to 2011 Datazones.

@@

[was this done after the previous stage or before? Would have thought before]

@@

```{r show_id_map, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
simd_2011_reweighted %>% 
  select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) %>% 
  tm_shape(.) + 
  tm_facets(ncol = 2) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) -> id_chor_dz2011

@@

simd_2011_reweighted %>% 
  select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  select(dz_2011, year, prop_id) %>% 
  left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
  filter(nearest_centre == "Glasgow") %>% 
  filter(distance_to_centre < 15000) %>% 
  select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) -> shp_jn

shp_jn <- shp_jn[!is.na(shp_jn$`2004`), ]
shp_jn %>% 
  tm_shape(.) + 
  tm_facets(ncol = 2) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) +
  tm_legend(legend.show = F) -> id_chor_dz2011_glasgow

@@

simd_2011_reweighted %>% 
  select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  select(dz_2011, year, prop_id) %>% 
  left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
  filter(nearest_centre == "Edinburgh") %>% 
  filter(distance_to_centre < 15000) %>% 
  select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) -> shp_jn

shp_jn <- shp_jn[!is.na(shp_jn$`2004`), ]
shp_jn %>% 
  tm_shape(.) + 
  tm_facets(ncol = 2) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) +
  tm_legend(legend.show = F) -> id_chor_dz2011_edinburgh

@@

simd_2011_reweighted %>% 
  select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  select(dz_2011, year, prop_id) %>% 
  left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
  filter(nearest_centre == "Dundee") %>% 
  filter(distance_to_centre < 15000) %>% 
  select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) -> shp_jn

shp_jn <- shp_jn[!is.na(shp_jn$`2004`), ]
shp_jn %>% 
  tm_shape(.) + 
  tm_facets(ncol = 2) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) +
  tm_legend(legend.show = F) -> id_chor_dz2011_dundee

@@

simd_2011_reweighted %>% 
  select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  select(dz_2011, year, prop_id) %>% 
  left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
  filter(nearest_centre == "Aberdeen") %>% 
  filter(distance_to_centre < 15000) %>% 
  select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) -> shp_jn

shp_jn <- shp_jn[!is.na(shp_jn$`2004`), ]
shp_jn %>% 
  tm_shape(.) + 
  tm_facets(ncol = 2) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) +
  tm_legend(legend.show = F) -> id_chor_dz2011_aberdeen

@@

```{r show_temporal_dep, echo = FALSE, warning = FALSE, EVAL = TRUE}

simd_2011_reweighted %>% 
  filter(year %in% c(2004, 2012)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2004 = `2004`, prop_id_2012 = `2012`) %>% 
  ggplot(., aes(x = prop_id_2004, y = prop_id_2012)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2004", y = "ID prop, 2012",
    title = "2012 against 2004"
       ) -> s_04_12

simd_2011_reweighted %>% 
  filter(year %in% c(2004, 2006)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2004 = `2004`, prop_id_2006 = `2006`) %>% 
  ggplot(., aes(x = prop_id_2004, y = prop_id_2006)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2004", y = "ID prop, 2006",
    title = "2006 against 2004"
       ) -> s_04_06

simd_2011_reweighted %>% 
  filter(year %in% c(2006, 2009)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2006 = `2006`, prop_id_2009 = `2009`) %>% 
  ggplot(., aes(x = prop_id_2006, y = prop_id_2009)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2006", y = "ID prop, 2009",
    title = "2009 against 2006"
    ) -> s_06_09

simd_2011_reweighted %>% 
  filter(year %in% c(2009, 2012)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2009 = `2009`, prop_id_2012 = `2012`) %>% 
  ggplot(., aes(x = prop_id_2009, y = prop_id_2012)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2009", y = "ID prop, 2012",
    title = "2012 against 2009"
  ) -> s_09_12

plot_grid(s_04_12, s_04_06, s_06_09, s_09_12, nrow = 2)

@@

```{r id_prop_by_year, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>%
    filter(distance_to_centre < 15000) %>% 
    group_by(nearest_centre, year) %>% 
    summarise(pop_total = sum(pop_total), pop_incomedeprived = sum(pop_incomedeprived)) %>% 
    mutate(prop_id = pop_incomedeprived / pop_total) %>% 
    mutate(prop_id = 100 * round(prop_id, 3)) %>% 
    select(City = nearest_centre, prop_id, Year = year) %>% 
    spread(Year, prop_id) %>% 
    ungroup() %>% 
    arrange(`2004`) %>% 
    kable(., format = "markdown", caption = "Income deprived % by City and Year")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Aberdeen", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Aberdeen")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Dundee", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Dundee")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Edinburgh", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Edinburgh")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Glasgow", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Glasgow")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Aberdeen", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Aberdeen")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Dundee", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Dundee")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Edinburgh", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Edinburgh")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Glasgow", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Glasgow")

>>>>

---
title: 'The Suburbanisation of Poverty in Scotland’s Cities: Urban Regeneration or
  Social Cleansing?'
author: "Jon Minton & Nick Bailey"
date: "31 August 2016"
output: word_document
---

@@

```{r id_props, eval = TRUE, echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE}

simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
    distinct() %>%
    rename(City = nearest_centre) %>% 
    filter(City %in% c("Aberdeen", "Dundee", "Edinburgh", "Glasgow")) %>% 
    mutate(
      lower_thresh = ifelse(City %in% c("Aberdeen", "Dundee"), 3200, 5000),
      centralness = ifelse(distance_to_centre < 20000, "periphery", "exurb"),
      centralness = ifelse(distance_to_centre < lower_thresh, "centre", centralness)
      ) %>% dplyr::select(-lower_thresh) %>% 
  filter(centralness %in% c("centre", "periphery")) %>% 
  group_by(City, year, centralness) %>%
  mutate(pop_nonid = pop_total - pop_incomedeprived) %>% 
  summarise(pop_nonid = sum(pop_nonid), pop_incomedeprived = sum(pop_incomedeprived)) %>% 
  summarise(
    `Income Deprived` = pop_incomedeprived[centralness == "centre"] / sum(pop_incomedeprived),
    `Not Income Deprived` = pop_nonid[centralness == "centre"] / sum(pop_nonid)
  ) %>% 
  gather(key = "type", value = "prop", `Income Deprived`:`Not Income Deprived`) -> tmp

tmp %>% filter(type == "Income Deprived") %>% 
  ggplot(., 
         aes(
            x = year, y = prop 
            )
         ) + 
  geom_line() + geom_point() +
  facet_wrap( ~ City, nrow = 2, scales = "free_y") + 
  labs(x = "Year", y = "Proportion", title = "Proportion income deprived near City Centre")

tmp %>% filter(type == "Not Income Deprived") %>% 
  ggplot(., 
         aes(
            x = year, y = prop 
            )
         ) + 
  geom_line() + geom_point() +
  facet_wrap( ~ City, nrow = 2, scales = "free_y") + 
  labs(x = "Year", y = "Proportion", title = "Proportion Not income deprived near City Centre")

@@

*	Converting data for 2004 to 2012 SIMDs from 2001 Datazones to 2011 Datazones.
*	Allocating Datazones to cities by defining a centroid for city, identifying the closest centroid for each Datazone and then applying a cut-off distance of around 18-20kms.

@@

@@

```{r show_id_map, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
simd_2011_reweighted %>% 
  dplyr::select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) %>% 
  tm_shape(.) + 
  tm_facets(ncol = 3) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012", "2016"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) -> id_chor_dz2011

@@

simd_2011_reweighted %>% 
  dplyr::select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
  filter(nearest_centre == "Glasgow") %>% 
  filter(distance_to_centre < 15000) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) -> shp_jn

shp_jn <- shp_jn[!is.na(shp_jn$`2004`), ]
shp_jn %>% 
  tm_shape(.) + 
  tm_facets(ncol = 3) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012", "2016"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) +
  tm_legend(legend.show = F) -> id_chor_dz2011_glasgow

@@

simd_2011_reweighted %>% 
  dplyr::select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
  filter(nearest_centre == "Edinburgh") %>% 
  filter(distance_to_centre < 15000) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) -> shp_jn

shp_jn <- shp_jn[!is.na(shp_jn$`2004`), ]
shp_jn %>% 
  tm_shape(.) + 
  tm_facets(ncol = 3) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012", "2016"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) +
  tm_legend(legend.show = F) -> id_chor_dz2011_edinburgh

@@

simd_2011_reweighted %>% 
  dplyr::select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
  filter(nearest_centre == "Dundee") %>% 
  filter(distance_to_centre < 15000) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) -> shp_jn

shp_jn <- shp_jn[!is.na(shp_jn$`2004`), ]
shp_jn %>% 
  tm_shape(.) + 
  tm_facets(ncol = 3) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012", "2016"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) +
  tm_legend(legend.show = F) -> id_chor_dz2011_dundee

@@

simd_2011_reweighted %>% 
  dplyr::select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
  filter(nearest_centre == "Aberdeen") %>% 
  filter(distance_to_centre < 15000) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) -> shp_jn

shp_jn <- shp_jn[!is.na(shp_jn$`2004`), ]
shp_jn %>% 
  tm_shape(.) + 
  tm_facets(ncol = 3) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012", "2016"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) +
  tm_legend(legend.show = F) -> id_chor_dz2011_aberdeen

@@

```{r show_temporal_dep, echo = FALSE, warning = FALSE, EVAL = TRUE}
simd_2011_reweighted %>% 
  filter(year %in% c(2004, 2016)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2004 = `2004`, prop_id_2016 = `2016`) %>% 
  ggplot(., aes(x = prop_id_2004, y = prop_id_2016)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2004", y = "ID prop, 2016",
    title = "2016 against 2004"
       ) -> s_04_16

simd_2011_reweighted %>% 
  filter(year %in% c(2004, 2006)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2004 = `2004`, prop_id_2006 = `2006`) %>% 
  ggplot(., aes(x = prop_id_2004, y = prop_id_2006)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2004", y = "ID prop, 2006",
    title = "2006 against 2004"
       ) -> s_04_06

simd_2011_reweighted %>% 
  filter(year %in% c(2006, 2009)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2006 = `2006`, prop_id_2009 = `2009`) %>% 
  ggplot(., aes(x = prop_id_2006, y = prop_id_2009)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2006", y = "ID prop, 2009",
    title = "2009 against 2006"
    ) -> s_06_09

simd_2011_reweighted %>% 
  filter(year %in% c(2009, 2012)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2009 = `2009`, prop_id_2012 = `2012`) %>% 
  ggplot(., aes(x = prop_id_2009, y = prop_id_2012)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2009", y = "ID prop, 2012",
    title = "2012 against 2009"
  ) -> s_09_12

simd_2011_reweighted %>% 
  filter(year %in% c(2012, 2016)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2012 = `2012`, prop_id_2016 = `2016`) %>% 
  ggplot(., aes(x = prop_id_2012, y = prop_id_2016)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2012", y = "ID prop, 2016",
    title = "2016 against 2012"
  ) -> s_12_16

plot_grid(s_04_16, s_04_06, s_06_09, s_09_12, s_12_16, nrow = 2)

@@

```{r id_prop_by_year, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>%
    filter(distance_to_centre < 15000) %>% 
    group_by(nearest_centre, year) %>% 
    summarise(pop_total = sum(pop_total), pop_incomedeprived = sum(pop_incomedeprived)) %>% 
    mutate(prop_id = pop_incomedeprived / pop_total) %>% 
    mutate(prop_id = 100 * round(prop_id, 3)) %>% 
    dplyr::select(City = nearest_centre, prop_id, Year = year) %>% 
    spread(Year, prop_id) %>% 
    ungroup() %>% 
    arrange(`2004`) %>% 
    kable(., format = "markdown", caption = "Income deprived % by City and Year")

The size of the income deprived population is shown below:

```{r id_size_by_year, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>%
    filter(distance_to_centre < 15000) %>% 
    group_by(nearest_centre, year) %>% 
    summarise(pop_incomedeprived = sum(pop_incomedeprived)) %>% 
    dplyr::select(City = nearest_centre, pop_incomedeprived, Year = year) %>% 
   mutate(pop_incomedeprived = round(pop_incomedeprived, 0)) %>% 
    spread(Year, pop_incomedeprived) %>% 
    ungroup() %>% 
    arrange(`2004`) %>% 
    kable(., format = "markdown", caption = "Income deprived size by City and Year")

And the size of the non-income deprived population is shown below:

```{r non_id_size_by_year, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>%
    filter(distance_to_centre < 15000) %>% 
    group_by(nearest_centre, year) %>% 
    summarise(pop_incomedeprived = sum(pop_incomedeprived),
              pop_total = sum(pop_total)
              ) %>%
    mutate(pop_nonincomedeprived = pop_total - pop_incomedeprived) %>% 
    dplyr::select(City = nearest_centre, pop_nonincomedeprived, Year = year) %>% 
   mutate(pop_nonincomedeprived = round(pop_nonincomedeprived, 0)) %>% 
    spread(Year, pop_nonincomedeprived) %>% 
    ungroup() %>% 
    arrange(`2004`) %>% 
    kable(., format = "markdown", caption = "Non-Income deprived size by City and Year")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Aberdeen", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  dplyr::select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  dplyr::select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Aberdeen")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Dundee", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  dplyr::select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  dplyr::select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Dundee")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Edinburgh", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  dplyr::select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  dplyr::select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Edinburgh")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Glasgow", measure == "RCI") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  dplyr::select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  dplyr::select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "RCI, Glasgow")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Aberdeen", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  dplyr::select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  dplyr::select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Aberdeen")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Dundee", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  dplyr::select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  dplyr::select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Dundee")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Edinburgh", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  dplyr::select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  dplyr::select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Edinburgh")

@@

```{r, eval = TRUE, echo = FALSE, warning = FALSE, results = 'asis'}
posterior_summaries %>% 
  ungroup() %>% 
  filter(place == "Glasgow", measure == "D") %>% 
  gather(key = "bound", value = "value", lower:upper) %>% 
  dplyr::select(period, bound, value) %>% 
  mutate(value = round(value, 3)) %>% 
  spread(bound, value) %>% 
  dplyr::select(period, median, lower, upper) %>% 
  kable(., format = "markdown", caption = "D, Glasgow")
